---
title: 'Project'
authors: "Naveenkumar Ramaraju, Rohit Dandona, Sravan Karumanchi, Srikrishna Charan Datla"
date: "Spring 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this project we are trying to figure out, what base attributes of Pokemon makes it most used by assesing overused(Standard class) Pokemons battle data and random battle data where any Pokemon can fight with any Pokemon randomly.

First we attempted to understand the attributes in the data set and its distribution. 

```{r}
library(ggplot2)
library(GGally)
library(tidyr)
library(gridExtra)
library(arm)
getwd()
```



```{r}
Pokemon.Attributes = read.csv('data/Pokeys.csv')
OverUsed = read.csv('data/gen7ou-0.txt',skip = 2)
OverUsed1500 = read.csv('data/gen7ou-1500.txt',skip = 2)
OverUsed1695 = read.csv('data/gen7ou-1695.txt',skip = 2)
OverUsed1825 = read.csv('data/gen7ou-1825.txt',skip = 2)
UnderUsed = read.csv('data/gen7uu-0.txt',skip = 2)
RandomBattle = read.csv('data/gen7randombattle-0.txt',skip = 2)
Uber = read.csv('data/gen7ubers-0.txt',skip = 2)
LC = read.csv('data/gen7lc-0.txt',skip = 2)
OUPokemon <- merge(Pokemon.Attributes,OverUsed,by="Pokemon")
RUPokemon <- merge(Pokemon.Attributes,RandomBattle,by="Pokemon")

```



```{r}
attach(OUPokemon)
ggpairs(data.frame(HP, Attack, Defense, Sp.Attack,Sp.Defense, Special, BST, Raw))
attach(RUPokemon)
ggpairs(data.frame(HP, Attack, Defense, Sp.Attack,Sp.Defense, Special, BST, Raw))
```




Now let's try a *histogram*:

```{r}
ggplot(Pokemon.Attributes,aes(x=Type.1,fill=Usage.Category)) + geom_histogram(stat="count")
ggplot(Pokemon.Attributes,aes(x=Type.1,y=HP)) + geom_boxplot()
ggplot(Pokemon.Attributes,aes(x=Type.1,y=Attack)) + geom_boxplot()+guides(fill=FALSE)
ggplot(Pokemon.Attributes,aes(x=Type.1,y=Defense)) + geom_boxplot()+guides(fill=FALSE)
ggplot(Pokemon.Attributes,aes(x=Type.1,y=BST)) + geom_boxplot()+guides(fill=FALSE)

attach(Pokemon.Attributes)
ggplot(data = as.data.frame(table(Type.1,Type.2)), aes(x = Type.1, y = Type.2)) +geom_tile(aes(fill=Freq))+ scale_fill_distiller(palette="Spectral") + ggtitle("Type 1 vs Type 2 - with no Type.2 as blank") + theme(plot.title = element_text(hjust = 0.5))


type1_type_2 = as.data.frame(table(Type.1,Type.2))
type1_type_2 <- type1_type_2[(type1_type_2$Type.2 != ''),]
ggplot(data = type1_type_2, aes(x = Type.1, y = Type.2,fill=Freq)) + geom_tile() + scale_fill_distiller(palette="Spectral") + ggtitle("Type 1 vs Type 2 - when Type 2 available") + theme(plot.title = element_text(hjust = 0.5))



ggplot(Pokemon.Attributes,aes(x=Generation,fill=Usage.Category)) + geom_histogram(stat="count")
ggplot(Pokemon.Attributes,aes(x=factor(Generation),y=HP,fill=Usage.Category)) + geom_boxplot()
ggplot(Pokemon.Attributes,aes(x=factor(Generation),y=Attack)) + geom_boxplot()+guides(fill=FALSE)
ggplot(Pokemon.Attributes,aes(x=factor(Generation),y=Defense)) + geom_boxplot()+guides(fill=FALSE)
ggplot(Pokemon.Attributes,aes(x=factor(Generation),y=BST)) + geom_boxplot()+guides(fill=FALSE)
ggplot(Pokemon.Attributes,aes(x=factor(Generation),y=BST,fill=Usage.Category)) + geom_boxplot()
```


```{r}
ggplot(Pokemon.Attributes, aes(x = Attack, y = Type.1)) + geom_point() + theme(axis.text.y = element_text(size = 7)) + facet_wrap(~factor(Generation), ncol = 1)
ggplot(Pokemon.Attributes, aes(x = Defense, y = Type.1)) + geom_point() + theme(axis.text.y = element_text(size = 7)) + facet_wrap(~factor(Generation), ncol = 1)
ggplot(Pokemon.Attributes, aes(x = BST, y = Type.1)) + geom_point() + theme(axis.text.y = element_text(size = 7)) + facet_wrap(~factor(Generation), ncol = 2)
detach(Pokemon.Attributes)
detach(OUPokemon)
detach(RUPokemon)
```



```{r}
OUPokemon <- merge(Pokemon.Attributes,OverUsed,by="Pokemon")
#OUPokemon <- OUPokemon[order(OUPokemon$Raw,decreasing = TRUE),]
RUPokemon <- merge(Pokemon.Attributes,RandomBattle,by="Pokemon")
UUPokemon <- merge(Pokemon.Attributes,UnderUsed,by="Pokemon")
UberPokemon <- merge(Pokemon.Attributes,Uber,by="Pokemon")
LCPokemon <- merge(Pokemon.Attributes,LC,by="Pokemon")

ggplot(OUPokemon, aes(x = Raw)) + geom_histogram()

summary(OUPokemon$Raw)

ggplot(OUPokemon, aes(x = Raw, color = factor(Usage.Category), fill = factor(Usage.Category))) + geom_histogram()

ggplot(OUPokemon, aes(x = Raw, color = factor(Usage.Category), fill = factor(Usage.Category))) + geom_histogram() + facet_wrap(~Usage.Category, ncol = 1)

ggplot(OUPokemon, aes(x = log(Raw), color = factor(Usage.Category), fill = factor(Usage.Category))) + geom_histogram() + facet_wrap(~Usage.Category, ncol = 1)

ggplot(OUPokemon, aes(x = Raw, color = factor(Generation), fill = factor(Generation))) + geom_histogram() + facet_wrap(~Generation, ncol = 1)

ggplot(OUPokemon, aes(x = log(Raw), color = factor(Generation), fill = factor(Generation))) + geom_histogram() + facet_wrap(~Generation, ncol = 1)

ggplot(OUPokemon, aes(x = Raw, color = factor(Type.1), fill = factor(Type.1))) + geom_histogram() + facet_wrap(~Type.1, ncol = 1)

ggplot(OUPokemon, aes(x = log(Raw), color = factor(Type.1), fill = factor(Type.1))) + geom_histogram() + facet_wrap(~Type.1, ncol = 1)

pOU <- ggplot(OUPokemon, aes(x=log2(Raw), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pUU <- ggplot(UUPokemon, aes(x=log2(Raw), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pUber <- ggplot(UberPokemon, aes(x=log2(Raw), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pLC <- ggplot(LCPokemon, aes(x=log2(Raw), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pRandom <- ggplot(RUPokemon, aes(x=log2(Raw), fill=Usage.Category, color=Usage.Category)) + geom_histogram()

pOURe <- ggplot(OUPokemon, aes(x=log2(Real+1), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pUURe <- ggplot(UUPokemon, aes(x=log2(Real+1), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pUberRe <- ggplot(UberPokemon, aes(x=log2(Real+1), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pLCRe <- ggplot(LCPokemon, aes(x=log2(Real+1), fill=Usage.Category, color=Usage.Category)) + geom_histogram()
pRandomRe <- ggplot(RUPokemon, aes(x=log2(Real+1), fill=Usage.Category, color=Usage.Category)) + geom_histogram()

#grid.arrange(pUber, pOU, pUU, pLC, pRandom)
grid.arrange(pUber,pUberRe, pOU,pOURe, pUU,pUURe, pLC,pLCRe, pRandom,pRandomRe, ncol=2)
ggplot(Pokemon.Attributes,aes(x=Usage.Category,fill=factor(Generation))) + geom_histogram(stat="count")

pOU <- ggplot(OUPokemon, aes(x=log2(Raw), fill=factor(Generation), color=factor(Generation))) + geom_histogram()
pUU <- ggplot(UUPokemon, aes(x=log2(Raw), fill=factor(Generation), color=factor(Generation))) + geom_histogram()
pUber <- ggplot(UberPokemon, aes(x=log2(Raw), fill=factor(Generation), color=factor(Generation))) + geom_histogram()
pLC <- ggplot(LCPokemon, aes(x=log2(Raw), fill=factor(Generation), color=factor(Generation))) + geom_histogram()
pRandom <- ggplot(RUPokemon, aes(x=log2(Raw), fill=factor(Generation), color=factor(Generation))) + geom_histogram()

grid.arrange(pUber, pOU, pUU, pLC, pRandom)


pOU <- ggplot(OUPokemon[(OUPokemon$Real.percentage > 2),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 10)
pUU <- ggplot(UUPokemon[(UUPokemon$Real.percentage > 2),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 10)
pUber <- ggplot(UberPokemon[(UberPokemon$Real.percentage > 2),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 10)
pLC <- ggplot(LCPokemon[(LCPokemon$Real.percentage > 2),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 10)
pRandom <- ggplot(RUPokemon[(RUPokemon$Real.percentage > 1),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 10)

grid.arrange(pUber, pOU, pUU, pLC, pRandom)


#pOU <- ggplot(OUPokemon[(OUPokemon$Real.percentage > 10),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 5)
#pUU <- ggplot(UUPokemon[(UUPokemon$Real.percentage > 10),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 5)
#pUber <- ggplot(UberPokemon[(UberPokemon$Real.percentage > 10),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 10)
#pLC <- ggplot(LCPokemon[(LCPokemon$Real.percentage > 10),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 5)
#pRandom <- ggplot(RUPokemon[(RUPokemon$Real.percentage > 1.3),], aes(x=Real.percentage, fill=factor(Generation), color=factor(Generation))) + geom_histogram(bins = 5)

#grid.arrange(pUber, pOU, pUU, pLC, pRandom)
```


```{r}
ggplot(OUPokemon, aes(x = BST, y = log(Real+1), color = factor(Generation))) + geom_point()
ggplot(OUPokemon, aes(x = Attack, y = log(Real+1), color = factor(Generation))) + geom_point()
ggplot(OUPokemon, aes(x = Defense, y = log(Real+1), color = factor(Generation))) + geom_point()





#ggplot(OUPokemon, aes(x = BST, y = log(Real+1), color = Ability.1)) + geom_point()
#ggplot(OUPokemon, aes(x = BST, y = log(Real+1), group = Ability.1, color = Ability.1)) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
```


```{r}
ggplot(UberPokemon, aes(x = BST, y = log(Real+1), group = Generation, color = factor(Generation))) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
ggplot(OUPokemon, aes(x = BST, y = log(Real+1), group = Generation, color = factor(Generation))) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
ggplot(UUPokemon, aes(x = BST, y = log(Real+1), group = Generation, color = factor(Generation))) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
ggplot(RUPokemon, aes(x = BST, y = log(Real+1), group = Generation, color = factor(Generation))) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
```


```{r}
ggplot(OUPokemon, aes(x = BST, y = log(Real+1), color = Type.1)) + geom_point()
ggplot(OUPokemon, aes(x = BST, y = log(Real+1), group = Type.1, color = Type.1)) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
```


```{r}
ggplot(OUPokemon, aes(x = BST, y = log(Real+1), group = Types, color = factor(Types))) + geom_point() + geom_smooth(method.args = list(degree = 1), se=FALSE)
```


```{r}
constant.glm = glm(Raw ~ 1, family = poisson, data = OUPokemon)
display(constant.glm)
```

```{r}
offset.glm = glm(Raw ~ 1, family = poisson, offset = log(BST), data = OUPokemon)
display(offset.glm)
```

```{r}
bst.glm = glm(Raw ~ BST, family = poisson, data = OUPokemon)
display(bst.glm)
```

```{r}
bst.UC.glm = glm(Raw ~ Attack + Defense + Special + Sp.Attack + Sp.Defense + HP +factor(Usage.Category) + factor(Generation), family = poisson, data = OUPokemon)
deviance(bst.UC.glm)
```

```{r}
fitted = fitted.values(bst.UC.glm)
resid = residuals(bst.UC.glm, type = "response")
df = data.frame(OUPokemon, .fitted = fitted, .resid = resid)
ggplot(df, aes(x = .fitted, y = .resid)) + geom_point() + geom_smooth(span = 1, method.args = list(degree = 1))
```

```{r}
std.resid = resid/sqrt(fitted)
df$.std.resid = std.resid
ggplot(df, aes(x = log(.fitted), y = .std.resid)) + geom_point() + geom_smooth(span = 1, method.args = list(degree = 1))

```

```{r}
overdispersion = sum(std.resid^2)/df.residual(bst.UC.glm)
overdispersion
sim1 = rpois(nrow(OUPokemon), lambda = fitted.values(bst.UC.glm))
summary(sim1)
summary(OUPokemon$Raw)

p1  <- ggplot(OUPokemon, aes(x = Raw)) + geom_histogram()
p2 <- ggplot(data.frame(sim1), aes(x = sim1)) + geom_histogram()
grid.arrange(p1, p2)

```

TO DO - Attack, Defense, usage - 3d plot???

Try - linear models or quasi poisson/Negative binomial regression/loess and GAM

```{r}
constant.glm = glm(Raw ~ 1, family = poisson, data = UberPokemon)
display(constant.glm)
```

```{r}
offset.glm = glm(Raw ~ 1, family = poisson, offset = log(BST), data = UberPokemon)
display(offset.glm)
```

```{r}
bst.glm = glm(Raw ~ BST, family = poisson, data = UberPokemon)
display(bst.glm)
```

```{r}
bst.UC.glm = glm(Raw ~ Attack + Defense + Special + Sp.Attack + Sp.Defense + HP +factor(Usage.Category) + factor(Generation), family = poisson, data = UberPokemon)
deviance(bst.UC.glm)
```

```{r}
fitted = fitted.values(bst.UC.glm)
resid = residuals(bst.UC.glm, type = "response")
df = data.frame(UberPokemon, .fitted = fitted, .resid = resid)
ggplot(df, aes(x = .fitted, y = .resid)) + geom_point() + geom_smooth(span = 1, method.args = list(degree = 1))
```

```{r}
std.resid = resid/sqrt(fitted)
df$.std.resid = std.resid
ggplot(df, aes(x = log(.fitted), y = .std.resid)) + geom_point() + geom_smooth(span = 1, method.args = list(degree = 1))

```

```{r}
overdispersion = sum(std.resid^2)/df.residual(bst.UC.glm)
overdispersion
sim1 = rpois(nrow(UberPokemon), lambda = fitted.values(bst.UC.glm))
summary(sim1)
summary(UberPokemon$Raw)

p1  <- ggplot(UberPokemon, aes(x = Raw)) + geom_histogram(breaks = seq(0, 200000, 5000))
p2 <- ggplot(data.frame(sim1), aes(x = sim1)) + geom_histogram(breaks = seq(0, 200000, 5000))
grid.arrange(p1, p2)
```



Gen - 1

```{r}
OverUsedG1 = read.csv('data/gen1ou-0.txt',skip = 2)
OverUsedG1 <- merge(Pokemon.Attributes,OverUsedG1,by="Pokemon")
constant.glm = glm(Raw ~ 1, family = poisson, data = OverUsedG1)
display(constant.glm)
```

```{r}
offset.glm = glm(Raw ~ 1, family = poisson, offset = log(BST), data = OverUsedG1)
display(offset.glm)
```

```{r}
bst.glm = glm(Raw ~ BST, family = poisson, data = OverUsedG1)
display(bst.glm)
```

```{r}
#bst.UC.glm = glm(Raw ~ Attack + Defense + Special + Sp.Attack + Sp.Defense + HP +factor(Usage.Category) + factor(Generation), family = poisson, data = OverUsedG1)
#deviance(bst.UC.glm)
```

```{r}
#fitted = fitted.values(bst.UC.glm)
#resid = residuals(bst.UC.glm, type = "response")
#df = data.frame(OverUsedG1, .fitted = fitted, .resid = resid)
#ggplot(df, aes(x = .fitted, y = .resid)) + geom_point() + geom_smooth(span = 1, method.args = list(degree = 1))
```

```{r}
#std.resid = resid/sqrt(fitted)
#df$.std.resid = std.resid
#ggplot(df, aes(x = log(.fitted), y = .std.resid)) + geom_point() + geom_smooth(span = 1, method.args = list(degree = 1))

```

```{r}
#overdispersion = sum(std.resid^2)/df.residual(bst.UC.glm)
#overdispersion
#sim1 = rpois(nrow(OverUsedG1), lambda = fitted.values(bst.UC.glm))
#summary(sim1)
#summary(OverUsedG1$Raw)

#p1  <- ggplot(OverUsedG1, aes(x = Raw)) + geom_histogram(breaks = seq(0, 50000, 1000))
#p2 <- ggplot(data.frame(sim1), aes(x = sim1)) + geom_histogram(breaks = seq(0, 50000, 1000))
#grid.arrange(p1, p2)
```
